Impact of Demographics and Skills of the Observer on Visual Statistical Inference

### 2013-05-30 sociology_paper.tex
link for gamma response updated

For $Y_{l,i}$ being binary response we use {\it logit} link function $g(\pi)=\log(\pi) - \log(1-\pi); 0 \le \pi \le 1$ and $\hat p_{\ell i}$ gives the estimate of proportion correct by subject $i$ with lineup $\ell$. For continuous response  $Y_{l,i}$ we use gamma link function and $\hat p_{\ell i}$ gives the estimate of mean time taken by subject $i$ for lineup $\ell$.

>>>>

For $Y_{l,i}$ being binary response we use {\it logit} link function $g(\mu)=g_1(\mu)=\log(\mu) - \log(1-\mu); 0 \le \mu \le 1$ and $\hat p_{\ell i}$ gives the estimate of proportion correct by subject $i$ with lineup $\ell$.  The response time taken is a positive random variable with a right skewed distribution. For this the usual convention is to model a gamma distribution with time. Thus we used inverse link function $g(\mu)=g_2(\mu)=1/\mu;  \mu >0$ for gamma response $Y_{l,i}$ and $\hat p_{\ell i}$ gives the estimate of mean time taken by subject $i$ for lineup $\ell$.
